Reply To Examiners

### 2014-05-14 answer_thesis_examiner/chap3.tex
auto

In this chapter, the Examiner wonder: ``if the proposed models are far from complete, how can it be an accurate representation of the data''.
To clarify, the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...

>>>>

\replyToComment
    {If the proposed models are ``far from complete'', how can it be an accurate representation of the data.}
    {the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...
}

%In this chapter, the Examiner wonder: ``if the proposed models are far from complete, how can it be an accurate representation of the data''.
%To clarify, the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
%Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
%They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
%  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...

\replyToComment
    {Page 133, line 3: ``it is definitely not fully representative of the data.''.
      So what kind of error it cause?
      How will it affects the use of your model?
      It is neccessary to point out what are the shortcomings and how it affects the use of your model!
    }
    {
      The thesis clearly indicated that the proposed models inherently suffer from loss of dimension where the full data is multi-dimensional and the proposed models are scalar.
}
